---
title: "glmmBoot"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

`glmmBoot` consists of a series of tools that for fitting and bootstrapping generalized linear mixed models (GLMMs) that takes advantage of the Template Model Builder (`TMB`), built on` CppAD` and `Eigen`. 

At this stage of development it can handle Mixed Logit and Mixed Poisson Models, yet it has the potential of being extended intended to handle a wide range of statistical distributions. 

# Mixed Poisson Example

This code to illustrates the implementation of the bootstrapping methods described in [(Flores-Agreda and Cantoni, Under Review)](https://www.researchgate.net/publication/315768128_Bootstrapping_Generalized_Linear_Mixed_Models_via_a_Weighted_Laplace_Approximation) in a real-data context. Data comes from the \emph{Epilepsy} example found in [Molenberghs & Verbeke (2006)](https://www.springer.com/gp/book/9780387251448) initially reported by [Faught et. al. (1996)](https://www.ncbi.nlm.nih.gov/pubmed/8649570). 


## Analysis

To start performing the analysis, you need:

1. the following packages:
```{r, message=FALSE, warnings=FALSE}
library(lme4)
library(glmmTMB)
library(sas7bdat)
library(TMB)
library(dplyr)
library(ggplot2)
```

2. to compile `glmm_rirs.cpp` and load the resulting binary into the environment:
```{r, message=FALSE}
compile(file = "glmmBoot/src/glmm_rirs.cpp")
```

```{r, message=FALSE}
dyn.load(dynlib("glmmBoot/src/glmm_rirs"))
```

3. the functions in the file `glmmBoot.R`:
```{r}
source("glmmBoot/R/glmmBoot.R")
```

4. the dataset `epilepsy.sas7bdat`
```{r}
epilepsy <- read.sas7bdat(file = "glmmBoot/data/epilepsy.sas7bdat")
```

